\huge\bf{Querypoint} : Moving Backwards on Wrong Values in the Buggy Execution

### 2011-06-10 trunk/papers/fse-tool2011/sig-alternate.tex

\textit{Querypoint}, is a Firefox plugin which enhances the popular 
Firebug JavaScript debugger with a new, practical feature called 
\textit{lastChange}. \textit{lastChange} automatically locates the last point that 
a variable or an object property has been changed. Starting from a 
program halted on a breakpoint, the \textit{lastChange} algorithm 
applies queries to the live program during re-execution, recording 
the call stack and limited program state each time 
the property value changes. When the program halts again on the breakpoint, 
it shows the program state at the last change point. To evaluate the usability and effectivness 
of \textit{Querypoint} we studied four experienced JavaScript developers applying the tool to two test cases.

@@

Locating the origin of wrong values becomes even harder when developers 
deal with weakly-typed dynamic languages such as JavaScript. First, due to weakly-typed
nature of these languages the search space that the developer should consider is considerably 
larger than traditional languages such as Java and C{\small\#}. Second, dynamic features make 
program full static analysis almost impossible.

@@

\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
  panel is selected; it gives access to
  all loaded source files and allows breakpoints to be set on lines. In this
  figure, the execution is paused at line 22 by a regular
  breakpoint. The Watch panel on the right shows the program state at
  the paused
  point. Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}. ]{\label{fig:example1}\includegraphics[width=1.0\textwidth, %height=.17\textheight
  ]{1-bp22.jpg}}

\subfigure[The result of \textit{lastChange} query for
  \texttt{myObject.myProperty}. The left panel, QP, shows the source
  code at the point of \textit{lastChange}; The right panel,
  TraceData, shows the collected data at the
  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
  ]{3-lastChange.jpg}}

\subfigure[The result of \textit{lastChange} query for
  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
  enter the expression in the watch box and after re-execution the result is available.
  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
  the list shows the corresponding code and
  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
    ]{4-lastChange2.jpg}}

@@

\mbox{\href{http://code.google.com/p/querypoint-debugging}{http://code.google.com/p/querypoint-debugging}}

>>>>

\textit{Querypoint}, is a Firefox plugin which enhances the popular 
Firebug JavaScript debugger with a new, practical feature called 
\textit{lastChange}. \textit{lastChange} automatically locates the last point that 
a variable or an object property has been changed. Starting from a 
program halted on a breakpoint, the \textit{lastChange} algorithm 
applies queries to the live program during re-execution, recording 
the call stack and limited program state each time 
the property value changes. When the program halts again on the breakpoint, 
it shows the call stack and program state at the last change point. To evaluate the usability and effectivness 
of \textit{Querypoint} we studied four experienced JavaScript developers applying the tool to two test cases.

@@

Locating the origin of wrong values becomes even harder when developers 
deal with weakly-typed dynamic languages such as JavaScript. First, due to weakly-typed
nature of these languages the search space that the developer should consider is considerably 
larger than traditional languages such as Java and C{\small\#}. Second, dynamics features limit 
the value of traditional compile-time program analysis.

@@

\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
  panel is selected; it gives access to
  all loaded source files and allows breakpoints to be set on lines. In this
  figure, the execution is paused at line 22 by a regular
  breakpoint. The Watch panel on the right shows the program state at
  the paused
  point. Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}. ]{\label{fig:example1}\includegraphics[width=1.0\textwidth, %height=.17\textheight
  ]{1-bp22.png}}

\subfigure[The result of \textit{lastChange} query for
  \texttt{myObject.myProperty}. The left panel, QP, shows the source
  code at the point of \textit{lastChange}; The right panel,
  TraceData, shows the collected data at the
  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
  ]{3-lastChange.png}}

\subfigure[The result of \textit{lastChange} query for
  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
  enter the expression in the watch box and after re-execution the result is available.
  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
  the list shows the corresponding code and
  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
    ]{4-lastChange2.png}}

@@

\mbox{\href{http://sites.google.com/site/querypoint}{http://sites.google.com/site/querypoint}}
